### 2024-02-23 docs/projects/datavis/ggplot/repesenting.qmd
ggplot - rendered

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: ggplot.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="ggplot_files/md-default6.js" type="text/javascript"></script><script src="ggplot_files/md-default7.js" type="text/javascript"></script>

@@

# Exploring ggplot - DRAFT
Here we explore [ggplot2](https://ggplot2.tidyverse.org/) from Clojure. The goal is to eventually implement a similar grammar in Clojure.

@@

::: {.sourceClojure}
```clojure
(ns ggplot
  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
            [clojisr.v1.applications.plotting :as plotting]
            [scicloj.kindly.v4.kind :as kind]
            [clojure.walk :as walk]
            [tablecloth.api :as tc]
            [editscript.core :as editscript]
            [clojure.pprint :as pp]
            [clojure.string :as str]))
```
:::

@@

The base R library:

@@

<g id="surface445">

@@

```{=html}
<img src="ggplot_files/0.png" style="width:100%;" />
```

@@

```{=html}
<img src="ggplot_files/1.png" style="width:100%;" />
```

@@

```{=html}
<img src="ggplot_files/2.png" style="width:100%;" />
```

@@

```{=html}
<img src="ggplot_files/3.png" style="width:100%;" />
```

@@

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}
  {:aes_params [],
   :stat
   {:extra_params ["na.rm" "orientation"],
    :super :ggproto-method,
    :compute_group :ggproto-method,
    :required_aes ["x" "y"],
    :setup_params :ggproto-method,
    :dropped_aes ["weight"]},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
   :geom
   {:setup_params :ggproto-method,
    :super :ggproto-method,
    :draw_key :ggproto-method,
    :extra_params ["na.rm" "orientation"],
    :required_aes ["x" "y"],
    :draw_group :ggproto-method,
    :optional_aes ["ymin" "ymax"],
    :rename_size [true],
    :setup_data :ggproto-method,
    :default_aes
    {:colour ["#3366FF"],
     :fill ["grey60"],
     :linewidth [1.0],
     :linetype [1.0],
     :weight [1.0],
     :alpha [0.4]}},
   :stat_params
   {:na.rm [false],
    :method ["lm"],
    :n [80.0],
    :orientation [nil],
    :level [0.95],
    :fullrange [false],
    :se [true],
    :formula nil,
    :method.args [],
    :span [0.75]},
   :constructor {: nil, :method ["lm"]},
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet
 {:params
  {:dir ["h"],
   :nrow nil,
   :as.table [true],
   :free {:x [false], :y [false]},
   :drop [true],
   :strip.position ["top"],
   :ncol nil,
   :facets {:cyl [~ cyl]},
   :labeller
   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x55801151ed28&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
  :shrink [true],
  :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}

@@

::: {.printedClojure}
```clojure
[[[:facet :params]
  :+
  {:dir ["h"],
   :nrow nil,
   :as.table [true],
   :free {:x [false], :y [false]},
   :drop [true],
   :strip.position ["top"],
   :ncol nil,
   :facets {:cyl [~cyl]},
   :labeller
   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x55801151ed28&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]

@@

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params {:size [5.0]},
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping {:colour [~ cyl]},
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales
 {:scales
  [{:labels [],
    :scale_name ["position_c"],
    :breaks [],
    :call
    {:labels labels,
     :scale_name ["position_c"],
     :breaks breaks,
     :name name,
     :palette identity,
     :super ScaleContinuousPosition,
     :guide guide,
     :minor_breaks minor_breaks,
     :n.breaks n.breaks,
     : nil,
     :aesthetics [$ ggplot_global y_aes],
     :na.value na.value,
     :trans trans,
     :oob oob,
     :position position,
     :limits limits,
     :expand expand},
    :rescaler :ggproto-method,
    :name [],
    :palette :ggproto-method,
    :super :ggproto-method,
    :guide [],
    :minor_breaks [],
    :n.breaks nil,
    :aesthetics
    ["y"
     "ymin"
     "ymax"
     "yend"
     "yintercept"
     "ymin_final"
     "ymax_final"
     "lower"
     "middle"
     "upper"
     "y0"],
    :na.value [nil],
    :trans
    {:name ["identity"],
     :transform
     "function (x) \nx\n&lt;bytecode: 0x55800c808140&gt;\n&lt;environment: namespace:base&gt;\n",
     :inverse
     "function (x) \nx\n&lt;bytecode: 0x55800c808140&gt;\n&lt;environment: namespace:base&gt;\n",
     :breaks
     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x558011cf7cd0&gt;\n&lt;environment: 0x5580173bcb00&gt;\n",
     :minor_breaks
     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558011cff4b8&gt;\n&lt;environment: 0x5580173bcc88&gt;\n",
     :format
     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558011d098e0&gt;\n&lt;environment: 0x5580173bcdd8&gt;\n",
     :domain [##-Inf ##Inf]},
    :oob :ggproto-method,
    :position ["left"],
    :limits [20.0 30.0],
    :expand [],
    :range {:super :ggproto-method}}],
  :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}

@@

```{=html}
<img src="ggplot_files/4.png" style="width:100%;" />
```

@@

     "function (x) \nlog(x, base)\n&lt;bytecode: 0x55801c8071a8&gt;\n&lt;environment: 0x55801c3836c8&gt;\n",

@@

     "function (x) \nbase^x\n&lt;bytecode: 0x55801c807058&gt;\n&lt;environment: 0x55801c3836c8&gt;\n",

@@

     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x55801c8159d0&gt;\n&lt;environment: 0x55801c386a88&gt;\n",

@@

     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x558011cff4b8&gt;\n&lt;environment: 0x55801c38a500&gt;\n",

@@

     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x558011d098e0&gt;\n&lt;environment: 0x55801c38a3b0&gt;\n",

@@

```{=html}
<img src="ggplot_files/5.png" style="width:100%;" />
```

@@

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ggplot.clj">projects/noj/notebooks/ggplot.clj</a></small></small></pre></div>
```

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: repesenting.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="repesenting_files/md-default6.js" type="text/javascript"></script><script src="repesenting_files/md-default7.js" type="text/javascript"></script>

@@

# Using ggplot Clojure using ClojisR

@@

::: {.sourceClojure}
```clojure
(ns repesenting
  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
            [clojisr.v1.applications.plotting :as plotting]
            [scicloj.kindly.v4.kind :as kind]
            [clojure.walk :as walk]
            [tablecloth.api :as tc]
            [editscript.core :as editscript]
            [clojure.pprint :as pp]
            [clojure.string :as str]))
```
:::

@@

Requireing the base R library as a Clojure namespace:

@@

<g id="surface266">

@@

```{=html}
<img src="repesenting_files/0.png" style="width:100%;" />
```

@@

```{=html}
<img src="repesenting_files/1.png" style="width:100%;" />
```

@@

```{=html}
<img src="repesenting_files/2.png" style="width:100%;" />
```

@@

```{=html}
<img src="repesenting_files/3.png" style="width:100%;" />
```

@@

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}
  {:aes_params [],
   :stat
   {:extra_params ["na.rm" "orientation"],
    :super :ggproto-method,
    :compute_group :ggproto-method,
    :required_aes ["x" "y"],
    :setup_params :ggproto-method,
    :dropped_aes ["weight"]},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:se [true], :na.rm [false], :orientation [nil]},
   :geom
   {:setup_params :ggproto-method,
    :super :ggproto-method,
    :draw_key :ggproto-method,
    :extra_params ["na.rm" "orientation"],
    :required_aes ["x" "y"],
    :draw_group :ggproto-method,
    :optional_aes ["ymin" "ymax"],
    :rename_size [true],
    :setup_data :ggproto-method,
    :default_aes
    {:colour ["#3366FF"],
     :fill ["grey60"],
     :linewidth [1.0],
     :linetype [1.0],
     :weight [1.0],
     :alpha [0.4]}},
   :stat_params
   {:na.rm [false],
    :method ["lm"],
    :n [80.0],
    :orientation [nil],
    :level [0.95],
    :fullrange [false],
    :se [true],
    :formula nil,
    :method.args [],
    :span [0.75]},
   :constructor {: nil, :method ["lm"]},
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet
 {:params
  {:dir ["h"],
   :nrow nil,
   :as.table [true],
   :free {:x [false], :y [false]},
   :drop [true],
   :strip.position ["top"],
   :ncol nil,
   :facets {:cyl [~ cyl]},
   :labeller
   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode: 0x556feb092c18&gt;\n&lt;environment: namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"},
  :shrink [true],
  :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}

@@

::: {.printedClojure}
```clojure
[[[:facet :params]
  :+
  {:dir ["h"],
   :nrow nil,
   :as.table [true],
   :free {:x [false], :y [false]},
   :drop [true],
   :strip.position ["top"],
   :ncol nil,
   :facets {:cyl [~cyl]},
   :labeller
   "function (labels, multi_line = TRUE) \n{\n    labels &lt;- lapply(labels, as.character)\n    if (multi_line) {\n        labels\n    }\n    else {\n        collapse_labels_lines(labels)\n    }\n}\n&lt;bytecode:_ 0x556feb092c18&gt;\n&lt;environment:_ namespace:ggplot2&gt;\nattr(,\"class\")\n[1] \"function\" \"labeller\"\n"}]]

@@

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params {:size [5.0]},
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping {:colour [~ cyl]},
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor {: nil, :mapping {: nil, :color cyl}, :size [5.0]},
   :position {:compute_layer :ggproto-method, :super :ggproto-method},
   :data []}],
 :scales
 {:scales
  [{:labels [],
    :scale_name ["position_c"],
    :breaks [],
    :call
    {:labels labels,
     :scale_name ["position_c"],
     :breaks breaks,
     :name name,
     :palette identity,
     :super ScaleContinuousPosition,
     :guide guide,
     :minor_breaks minor_breaks,
     :n.breaks n.breaks,
     : nil,
     :aesthetics [$ ggplot_global y_aes],
     :na.value na.value,
     :trans trans,
     :oob oob,
     :position position,
     :limits limits,
     :expand expand},
    :rescaler :ggproto-method,
    :name [],
    :palette :ggproto-method,
    :super :ggproto-method,
    :guide [],
    :minor_breaks [],
    :n.breaks nil,
    :aesthetics
    ["y"
     "ymin"
     "ymax"
     "yend"
     "yintercept"
     "ymin_final"
     "ymax_final"
     "lower"
     "middle"
     "upper"
     "y0"],
    :na.value [nil],
    :trans
    {:name ["identity"],
     :transform
     "function (x) \nx\n&lt;bytecode: 0x556fe5ccb140&gt;\n&lt;environment: namespace:base&gt;\n",
     :inverse
     "function (x) \nx\n&lt;bytecode: 0x556fe5ccb140&gt;\n&lt;environment: namespace:base&gt;\n",
     :breaks
     "function (x, n = n_default) \n{\n    x &lt;- x[is.finite(x)]\n    if (length(x) == 0) {\n        return(numeric())\n    }\n    rng &lt;- range(x)\n    labeling::extended(rng[1], rng[2], n, ...)\n}\n&lt;bytecode: 0x556fe8978000&gt;\n&lt;environment: 0x556ff5d42868&gt;\n",
     :minor_breaks
     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556fe8974af0&gt;\n&lt;environment: 0x556ff5d46510&gt;\n",
     :format
     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556fe89717a0&gt;\n&lt;environment: 0x556ff5d463c0&gt;\n",
     :domain [##-Inf ##Inf]},
    :oob :ggproto-method,
    :position ["left"],
    :limits [20.0 30.0],
    :expand [],
    :range {:super :ggproto-method}}],
  :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["cyl"]}}

@@

```{=html}
<img src="repesenting_files/4.png" style="width:100%;" />
```

@@

     "function (x) \nlog(x, base)\n&lt;bytecode: 0x556feae855e8&gt;\n&lt;environment: 0x556ff3da9fc8&gt;\n",

@@

     "function (x) \nbase^x\n&lt;bytecode: 0x556feae85738&gt;\n&lt;environment: 0x556ff3da9fc8&gt;\n",

@@

     "function (x, n = n_default) \n{\n    raw_rng &lt;- suppressWarnings(range(x, na.rm = TRUE))\n    if (any(!is.finite(raw_rng))) {\n        return(numeric())\n    }\n    rng &lt;- log(raw_rng, base = base)\n    min &lt;- floor(rng[1])\n    max &lt;- ceiling(rng[2])\n    if (max == min) {\n        return(base^min)\n    }\n    by &lt;- floor((max - min)/n) + 1\n    breaks &lt;- base^seq(min, max, by = by)\n    relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= base^rng[2]\n    if (sum(relevant_breaks) &gt;= (n - 2)) {\n        return(breaks)\n    }\n    while (by &gt; 1) {\n        by &lt;- by - 1\n        breaks &lt;- base^seq(min, max, by = by)\n        relevant_breaks &lt;- base^rng[1] &lt;= breaks & breaks &lt;= \n            base^rng[2]\n        if (sum(relevant_breaks) &gt;= (n - 2)) {\n            return(breaks)\n        }\n    }\n    log_sub_breaks(rng, n = n, base = base)\n}\n&lt;bytecode: 0x556feae75a68&gt;\n&lt;environment: 0x556ff3dae4d0&gt;\n",

@@

     "function (b, limits, n) \n{\n    b &lt;- b[!is.na(b)]\n    if (length(b) &lt; 2) {\n        return()\n    }\n    bd &lt;- diff(b)[1]\n    if (!reverse) {\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    else {\n        if (max(limits) &gt; max(b)) \n            b &lt;- c(b[1] - bd, b)\n        if (min(limits) &lt; min(b)) \n            b &lt;- c(b, b[length(b)] + bd)\n    }\n    seq_between &lt;- function(a, b) {\n        seq(a, b, length.out = n + 1)[-(n + 1)]\n    }\n    breaks &lt;- unlist(Map(seq_between, b[-length(b)], b[-1]))\n    breaks &lt;- c(breaks, b[length(b)])\n    breaks\n}\n&lt;bytecode: 0x556fe8974af0&gt;\n&lt;environment: 0x556ff3dae118&gt;\n",

@@

     "function (x) \n{\n    if (!is.null(names(x))) {\n        return(names(x))\n    }\n    ret &lt;- format(x, ..., trim = TRUE, justify = \"left\")\n    ret[is.na(x)] &lt;- NA\n    ret\n}\n&lt;bytecode: 0x556fe89717a0&gt;\n&lt;environment: 0x556ff3dadfc8&gt;\n",

@@

```{=html}
<img src="repesenting_files/5.png" style="width:100%;" />
```

@@

```{=html}
<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/datavis/ggplot/notebooks/representing.clj">projects/datavis/ggplot/notebooks/representing.clj</a></small></small></pre></div>
```
